\input{../preamble}

\textbf{\color{red}Last updated: 2022/02/17}

\begin{tldr}
	\begin{itemize}
		\item{Fire good attacker krug}
		\item{Electric might be the best attacker, though, with Ice as also good}
		\item{Magic and Martial suck as attackers, but that's okay}
		\item{Earth and Void might be the best defenders, but Metal, Nature, and Water are good, too}
		\item{Some types have an immunity, but Electric is healed by other Electric Types instead of damaged}
	\end{itemize}
	Note: Types may be found, analyzed, and modified using an EditorUtilityWidget found under \texttt{Content/Editor/Type-Advantage}, right-clicking the \texttt{TypeAdvantages} widget, and selecting \texttt{Run Editor Utility Widget}.
\end{tldr}

\sect{Highs and Lows}

Note: ``immune'' and ``healed'' are grouped into ``ineffective'' (attacking) and ``resists'' (defending).

\subsect{Attacking}
\begin{itemize}
	\item{\textbf{Type with most effective attacks:} Fire (4)
		\begin{itemize}
			\item{Fire has a good number of ineffective attack (4; the same as its number of effective attacks).}
		\end{itemize}
	}
	\item{\textbf{Type with best ratio of effective-to-ineffective attacks:} Spirit (0:0) then Ice (3:2) and Electric (3:2, but those 2 are immune and healed by)
		\begin{itemize}
			\item{Electric might be a dominant Type, but that's okay. One of them should be dominant.}
			\item{Earth takes zero damage from it, making it a solid check (although Electric + Metal/Nature/Water might be a terrifying combination, with Electric + Nature being able to take on other Electric Types).}
		\end{itemize}
	}
	\item{\textbf{Type with the least effective attacks:} Magic (0)
		\begin{itemize}
			\item{Toxic deserves a special mention here as the only Type with zero attack against \textit{two} other Types (Poison and Metal). It has 3 effective attacks, though, making it not so bad.}
		\end{itemize}
	}
	\item{\textbf{Type with the worst ratio of effective-to-ineffective attacks:} Magic (0:1) then Martial (2:3)
		\begin{itemize}
			\item{It's okay that Magic and Martial suck. Magic should be used for utility reasons and Martial should be used for raw power.}
		\end{itemize}
	}
\end{itemize}

\subsect{Defending}
\begin{itemize}
	\item{\textbf{Type with the most resists:} Earth (4), Metal (4), Nature (4), Void (4), and Water (4).
		\begin{itemize}
			\item{This is way fewer than Pok\'{e}mon has. For example, Fire in Pok\'{e}mon has 6 resists, Poison has 5, and Steel has a whopping 10.}
			\item{To be fair, Pok\'{e}mon also has more types overall (18 vs our 15).}
			\item{Of ours, Earth and Void are the ``best'', since they only have 3 weaknesses and one of their resists is an immunity.}
		\end{itemize}
		\item{\textbf{Type with the most immunities:} Air (1), Earth (1), Metal (1), Toxic (1), and Void (1)
			\begin{itemize}
				\item{Electric gets a special mention as the only Type to have a ``healed by'' other Electric Types, which is better than being immune.}
			\end{itemize}
		}
	}
\end{itemize}

\sect{Fearsome Dual Types}

Attacking-wise, the following dual types have neutral STAB coverage:
\begin{itemize}
	\item{Air + Void (3 effective attacks)}
\end{itemize}

\sect{Rock-Paper-Scissors}

\input{../postamble}