\input{../standalone}

\begin{tldr}
	\begin{itemize}
		\item{Projectiles carry \code{MoveData} from a caster to a target.}
		\item{How Projectiles do this can be customized by writing your own scripts or Blueprints.}
	\end{itemize}
\end{tldr}

\localtoc

%====================================================

\sect{What Is a Projectile?}

A Projectile is a Actor Blueprint. It contains:
\begin{itemize}
	\item{A \code{UProjectileMove} that marries the physical Projectile with \code{MoveData}. This has required\\\code{UActorComponent}s:
		\begin{itemize}
			\item{\code{UProjectileDirection} to set the Projectile's direction (either initially or over time)}
			\item{\code{UProjectileSpeed} to set the Projectile's speed (either initially or over time)}
			\item{\code{UProjectileDamage} to control how the damage is doled out (e.g., single use vs multiple use)}
			\item{\code{UExpriationComponent} to control what happens when the Projectile's use comes to an end}
		\end{itemize}
	}
	\item{A \code{UProjectileMovementComponent} that controls how it moves. This should not normally be altered since its settings are more flexibly set by the aforementioned components.}
	\item{The Projectile's visuals, such as a static mesh or particle effects.}
	\item{The Projectile's collider, which includes shape, collision settings (like what the Projectile interacts with), and physics settings (like if the Projectile bounces).}
\end{itemize}
\noindent Of course, there might be other things there too for custom purposes. An additional note is that the \code{MoveData} is what decides the spawn location (via \code{UActorSpawnScheme}s).\\

While many of these are self-evident, a couple require explanation.

%====================================================

\sect{\code{UProjectileDirection}}

By default, the Projectile's direction is set immediately when spawned. This optionally includes the Projectile's rotation.

Usually, the direction is retrieved from \code{UCombatTargetingComponent}. This could be from the player; for example, mouse position gets a vector direction or mouseover gets an Actor to inflict a status on. \todo{While not implemented yet,} for non-players, this includes getting vectors or Actor targets via AI. 

By default, a \code{UProjectileDirection} does not tick, but it might be a good idea to make a derived class that does. Examples are seeking Projectiles or a Projectile that changes behavior (e.g., explodes) after a certain time or distance.

%====================================================

\sect{\code{UProjectileSpeed}}

This is incredibly similar to \code{UProjectileDirection}. You may want to tick it, for example, to have a Projectile that speeds up as it gets closer to its target.

%====================================================

\sect{\code{UExpirationComponent}}

\code{UExpirationComponent}s can be used on a variety of Actors, not just Projectiles. They delete an Actor after a set time or distance traveled. This could be used on not only Projectiles, but also limited-time events or objects that only appear in certain areas (and taking them outside that area deletes them).


Notably, they have one Outlet: \code{GetExpirationDistanceOutlet}. This may be useful for talents that make Projectiles last longer (for example, Junkrat's frag grenade launcher from Overwatch).

%====================================================

\postamble{}